---
output: 
  pdf_document:
    includes:
      in_header: latex_input/preamble.tex
---

```{r setup, include=FALSE}
options(knitr.table.format = "latex")
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	error = FALSE
)
meta <- participant$metadata
```

\begin{center}
\textbf{\large \textbf{La Trobe Performance Hub} }
\vspace{2ex   }
\end{center}
\begingroup
\setlength{\tabcolsep}{0.5em}
\begin{tabularx}{\textwidth}{r l}
\textbf{Athlete Name:} & `r meta$name`\\
\textbf{Age:} & `r meta$age`\\
\textbf{Body Mass:} & `r round(as.numeric(meta$bodyMass,digits=1))` kg\\
\textbf{Exercise Device:} & `r meta$device`\\
\end{tabularx}
\endgroup
\vspace{4ex}

\fancysection{Test Details}

```{r}
library(tidytable)
library(kableExtra)
options(kableExtra.latex.load_packages=T)
detailsTable <- participant$testDetails
detailsTable %>% 
  mutate(across(everything(),as.character)) %>% 
  mutate(across(everything(),~paste("\\raisebox{-1pt}{", ., "}")) ) %>% 
    kbl( booktabs = T, escape = FALSE,align = "c",
       col.names= c("Date of Test","Temperature (° C)","Humidity (\\%)","Pressure (mmHg)") ) %>% 
  kable_styling(latex_options = c("HOLD_position")) %>% 
  column_spec(1:4,width = "\\\\dimexpr\\\\textwidth/4\\\\relax") %>% 
    row_spec(1, background="#fff3f3")
```

\fancysection{Summary Data}

```{r}
summaryTable <- participant$summaryTable
summaryTable %>%
  mutate(across(everything(),as.character)) %>% 
  mutate(across(everything(),~paste("\\raisebox{-1pt}{", ., "}")) ) %>% 
  kbl( booktabs = T, escape = FALSE,align = "c",
       col.names= c("Variable","Power \\par (W)","Power \\par (\\%)",
                    "VO\\textsubscript{2} \\par (L/min)",
                    "VO\\textsubscript{2} \\par (mL/kg/min)",
                    "VO\\textsubscript{2max} \\par (\\%)",
                   "Heart Rate \\par (beats/min)",
                   "HR\\textsubscript{max} \\par (\\%)" ) ) %>% 
  kable_styling(latex_options = c("HOLD_position")) %>% 
  row_spec(seq(1,nrow(summaryTable),2), background="#fff3f3") %>% 
  column_spec(1:8,width = "\\\\dimexpr\\\\textwidth/8\\\\relax")
```

\fancysection{GXT Data}

```{r}
gxtTable <- participant$gxtTable
gxtTable %>%
  mutate(across(everything(),as.character)) %>%
  mutate(across(everything(),~paste("\\raisebox{-1pt}{", ., "}")) ) %>%
  kbl( booktabs = T, escape = FALSE,digits = 1, align = "c",linesep = "",
       col.names = c("Power \\par (W)","VO\\textsubscript{2} \\par (L/min)",
                     "VO\\textsubscript{2} \\par (mL/kg/min)",
                    "VO\\textsubscript{2max} \\par (\\%)",
                    "Heart Rate \\par (beats/min)",
                    "HR\\textsubscript{max} \\par (\\%)") ) %>%
  column_spec(1:6, width = "\\\\dimexpr\\\\textwidth/6\\\\relax") %>%
  row_spec(seq(1,nrow(gxtTable),2), background="#fff3f3") %>%
    kable_styling(latex_options=c("HOLD_position")) %>%
  footnote(number = "Power at the last stage is an approximation relative to the VO\\\\textsubscript{2} achieved.",escape = F)
```

\newpage
\fancysection{Training Zones - Modified Allen \& Coggan}

```{r}
cogganTable <- participant$cogganTable
coln <- colnames(cogganTable)
cogganTable %>% 
  tidytable::mutate(across(.cols = everything(),as.character)) %>% 
  tidytable::mutate(across(everything(),~paste("\\raisebox{-1pt}{", ., "}")) ) %>% 
  `colnames<-`(coln) %>% 
  kbl( booktabs = T, escape = FALSE,digits = 1, align = "c",linesep = "") %>% 
  add_header_above(c(" "=2, "(W)" = 2, "(beats/min)" = 2,"(Borg 6-20)" = 2),escape = F,
  align="c") %>%
  add_header_above(c(" "=2, "Power Zones" = 2, "Heart Rate Zones" = 2,"RPE" = 2),
                   line = F) %>%
  kable_styling(latex_options=c("HOLD_position")) %>% 
  column_spec(1, width = "\\\\dimexpr7\\\\textwidth/100\\\\relax") %>% 
  column_spec(2, width = "\\\\dimexpr24\\\\textwidth/100\\\\relax") %>% 
  column_spec(3:8, width = "\\\\dimexpr11.5\\\\textwidth/100\\\\relax") %>% 
  row_spec(seq(1,nrow(cogganTable),2), background="#fff3f3")
```

\fancysection{Training Zones - AIS}

```{r}
aisTable <- participant$aisTable
coln <- colnames(aisTable)
aisTable %>% 
  tidytable::mutate(across(.cols = everything(),as.character)) %>% 
  tidytable::mutate(across(everything(),~paste("\\raisebox{-1pt}{", ., "}")) ) %>% 
  `colnames<-`(coln) %>% 
  kbl( booktabs = T, escape = FALSE,digits = 1, align = "c",linesep = "") %>% 
      add_header_above(c(" "=2, "(W)" = 2, "(beats/min)" = 2,"(Borg 6-20)" = 2),escape = F,
      align="c") %>%
  add_header_above(c(" "=2, "Power Zones" = 2, "Heart Rate Zones" = 2,"RPE" = 2),
                   line = F) %>%
  kable_styling(latex_options=c("HOLD_position")) %>% 
  column_spec(1, width = "\\\\dimexpr7\\\\textwidth/100\\\\relax") %>% 
  column_spec(2, width = "\\\\dimexpr24\\\\textwidth/100\\\\relax") %>% 
  column_spec(3:8, width = "\\\\dimexpr11.5\\\\textwidth/100\\\\relax") %>% 
  row_spec(seq(1,nrow(aisTable),2), background="#fff3f3")
```
\newpage
\fancysection{GXT Plots}
```{r, out.width="100%", include=TRUE, fig.align="center"}
participantName <- participant$participantName
dir <- here::here("output","plots","gxt_plots")
filepath <- file.path(dir, paste0(participantName, ".pdf"))
knitr::include_graphics(filepath, rel_path = F)
```
\newpage
\fancysection{Threshold Plots}
```{r, out.width="100%", include=TRUE, fig.align="center"}

dir <- here::here("output","plots","threshold_plots")
filepath <- file.path(dir, paste0(participantName, ".pdf"))
knitr::include_graphics(filepath, rel_path = F)
```