---
output: 
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load(file = ".RData") 
library(kableExtra)
library(tidyverse) 
library(magrittr)
options(digits=2)
options(knitr.table.format = "latex")

```

\begin{center}
\textbf{\large \textbf{La Trobe Performance Hub} }
\end{center}
\vspace{2em}
\begin{tabularx}{\textwidth}{r c}
\textbf{Athlete Name:} & `r dem$NAME`\\
\textbf{Date of Birth:} & `r format(dem$TEST_DAT, format = "%d-%b-%Y")`\\
\textbf{Sport:} & \\
\end{tabularx}

\fancysection{Test Details}

\fancysection{Anthropometry Data}

\fancysection{Summary Data}
```{r, echo=FALSE}
cp %>% select(THRESHOLD,VO2:HRPERC) %>%
   set_colnames(c("Threshold","$VO_2$","Work","Heart Rate","$VO_2 (\\%)$",
                    "Work (\\%)", "Heart Rate (\\%)" ) ) %>% 
  kbl( booktabs = T, escape = FALSE) %>% 
  kable_styling(latex_options=c("HOLD_position"))
```
\fancysection{GXT Data}
```{r, echo=FALSE}

gxt %>%
  set_colnames(c("Power","$VO_2$(mL/kg/min)","Heart Rate (beats/min)","$VO_{2max} (\\%)$",
                 "$HR_{max} (\\%)$" ) ) %>% 
  kbl( booktabs = T, escape = FALSE) %>% 
  kable_styling(latex_options=c("HOLD_position","striped"))


```

\fancysection{Training Zones Modified Allen \& Coggan}



